Periodic Traveling Waves in an Integro-Difference Equation With a Nonmonotone Growth Function and Strong Allee Effect

### 2021-07-04 paper_draft_bare.tex
updates

\usepackage{amsmath,amsthm,amssymb}
\usepackage{hyperref}
%\usepackage{geometry}
\usepackage{graphicx}
\usepackage{enumerate}
%\usepackage{caption,subcaption}
\usepackage{caption}
\usepackage{subcaption}

@@

@@

Piecewise constant growth functions and uniform distributions have been used in the studies of integro-difference equations; see for example~\cite{kot1, lut,otto,  pnas}. We rigorously construct periodic traveling waves with periodic speeds for (\ref{q}). To the best of our knowledge, this is the first time that traveling waves with oscillating speeds have been analytically established  for scalar spatiotemporal equations with constant parameters. We also show the convergence of solutions with compactly supported initial data to translations of the traveling wave under appropriate conditions. Equation (\ref{q}) may be viewed as a symbolic model for integro-difference equations with a growth function exhibiting a strong Allee effect and a period two cycle. The results obtained this paper provide important insights into integro-difference equations with general growth functions.

\section{Results}

\subsection{Periodic traveling waves}

@@

\item  for all $\lambda\in(0,1)$, for all $a\in\mathbb R$, the function $x \mapsto k(x)-\lambda k(x-a)$ has at most one zero-crossing in $\mathbb R$.
\end{enumerate}

@@

 Let $w_1$ and $w_2$ be two functions defined by
\begin{equation} \label{w1}
w_1(x) := \int_x^\infty k(y) \, dy
\end{equation}
and
\begin{equation} \label{w2}
w_2(x) := Q[w_1](x+c^*) = \int_{-\infty}^{\infty} k(y) g(w_1(x+c^*-y)) \, dy 
\end{equation} 
with $c^* \in \mathbb R$ a constant given by
\begin{equation}
c^*=\frac{1}{2}\sup\{x\in\mathbb R\mid Q[w_1](x)\geq\a\}
\end{equation}

@@

\begin{lem} \label{lemma0}
$w_1(x)$ is monotone, while $w_2(x)$ has at most one turning point.
\end{lem}

\begin{proof}
The monotonicity of $w_1$ follows since $w_1'(x)=-k(x)\leq 0$ by hypothesis (H1). To count the turning points of $w_2$, let $x_\a=\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}$ and $x_\b=\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}$. Since $w_1$ is monotone, it follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$. Applying the integro-difference operator to $w_1$ yields
\begin{equation} \label{qw1calculation}
\begin{aligned}
Q[w_1](x) %&= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
&= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \int_{x_\b}^{x_\a} k(x-y) \, dy \\
%&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
&= \int_{x-x_\a}^{\infty} k(y) \, dy - (1-\m) \int_{x-x_\b}^{\infty} k(y) \, dy
\end{aligned} \end{equation}

Taking the derivative with respect to $x$, we find
\begin{equation}\label{dw2dx}
\frac{d}{dx}Q[w_1] = -k(x-x_\a) + (1-\m)k(x-x_\b)
\end{equation}

From hypothesis (H4), we can conclude that \eqref{dw2dx} has at most one zero-crossing, hence $w_2(x)$ has at most one turning point.
\end{proof}

@@

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{figures/fig2A.png}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{figures/fig2B.png}
  \label{fig:sub2}
\end{subfigure}
\caption{Plots of $w_1(x)$ (left) and $w_2(x)$ (right) with the Laplace dispersal kernel $k(x)=\frac{1}{2}e^{-|x|}$ and growth parameters $\alpha=0.3$, $\mu=0.5$, and $\beta=0.8$.}
\label{fig:test}
\end{figure}

@@

>>>>

\usepackage{amsmath,amsthm,amssymb}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{enumerate}
%\usepackage{caption,subcaption}
\usepackage{caption}
\usepackage{subcaption}

%\usepackage{newpxtext,newpxmath}
\usepackage{multicol}

@@

%\begin{multicols}{1}

@@

Piecewise constant growth functions have been used in the studies of integro-difference equations; see for example~\cite{kot1, lut,otto,  pnas}. We rigorously construct periodic traveling waves with periodic speeds for (\ref{q}). To the best of our knowledge, this is the first time that traveling waves with oscillating speeds have been analytically established  for scalar spatiotemporal equations with constant parameters. We also show the convergence of solutions with compactly supported initial data to translations of the traveling wave under appropriate conditions. Equation (\ref{q}) may be viewed as a symbolic model for integro-difference equations with a growth function exhibiting a strong Allee effect and a period two cycle. The results obtained this paper provide important insights into integro-difference equations with general growth functions.

%\section{Results}
\section{Periodic traveling waves}
%\subsection{Periodic traveling waves}

@@

\item  for all $\lambda\in(0,1)$, for all $a\in\mathbb R$, the equation $k(x)=\lambda k(x-a)$ has at most one real solution.
\end{enumerate}

@@

 Let $w_1$ and $w_2$ be two functions defined by
\begin{equation} \label{w1}
w_1(x) := \int_x^\infty k(y) \, dy
\end{equation}
and
\begin{equation} \label{w2}
w_2(x) = \int_x^\infty \left( k(y-x_\a) - (1-\mu)k(y-x_\b)\right) \, dy 
\end{equation} 
where $x_\a,x_\b$ and $c^* \in \mathbb R$ are constants given by
\begin{equation}
x_\a =\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}, \quad
x_\b =\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}
\end{equation}
and
\begin{equation}
c^*=\frac{1}{2}\sup\{x\in\mathbb R\mid Q[w_1](x)\geq\a\}
\end{equation}

@@

\begin{lem} \label{lemma0.5}
$Q[w_1](x) = w_2(x)$ for all $x\in\mathbb R$.
\end{lem}

\begin{proof}
$w_1$ is monotonically decreasing with $w_1(-\infty)=1$ and $w_1(\infty)=0$. It follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$. Applying the integro-difference operator yields
\begin{equation} \label{qw1calculation}
\begin{aligned}
Q[w_1](x) %&= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
&= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \int_{x_\b}^{x_\a} k(x-y) \, dy \\
%&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
&= \int_{x-x_\a}^{\infty} k(y) \, dy - (1-\m) \int_{x-x_\b}^{\infty} k(y) \, dy \\
&= \int_{x}^{\infty} \left(k(y-x_\a)  - (1-\m)k(y-x_\b)\right) \, dy
\end{aligned} \end{equation}
%It can now be seen that replacing $x$ with $x-c^*$ in equation \eqref{w2} produces \eqref{qw1calculation}.
\end{proof}

%
%\begin{lem} \label{lemma0}
%$w_1(x)$ is monotone, while $w_2(x)$ has at most one turning point.
%\end{lem}
%
%
%
%
%\begin{proof}
%The monotonicity of $w_1$ follows since $w_1'(x)=-k(x)\leq 0$ by hypothesis (H1). To count the turning points of $w_2$, let $x_\a=\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}$ and $x_\b=\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}$. Since $w_1$ is monotone, it follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$. Applying the integro-difference operator to $w_1$ yields
%\begin{equation} \label{qw1calculation}
%\begin{aligned}
%Q[w_1](x) %&= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
%&= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \int_{x_\b}^{x_\a} k(x-y) \, dy \\
%%&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
%&= \int_{x-x_\a}^{\infty} k(y) \, dy - (1-\m) \int_{x-x_\b}^{\infty} k(y) \, dy
%\end{aligned} \end{equation}
%
%Taking the derivative with respect to $x$, we find
%\begin{equation}\label{dw2dx}
%\frac{d}{dx}Q[w_1] = -k(x-x_\a) + (1-\m)k(x-x_\b)
%\end{equation}
%
%From hypothesis (H4), we can conclude that \eqref{dw2dx} has at most one zero-crossing, hence $w_2(x)$ has at most one turning point.
%\end{proof}

@@

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{figures/fig2A.png}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{figures/fig2B.png}
  \label{fig:sub2}
\end{subfigure}
\caption{The shape of the two periodic traveling wave profiles with Laplace dispersal kernel and growth parameters $\alpha=0.3$, $\mu=0.5$, and $\beta=0.8$.}
\label{fig:test}
\end{figure}

@@

%\end{multicols}

### 2021-07-04 paper_draftver6.tex
updates

\newcommand{\winva}{{w_1^{-1}(a)}}
\newcommand{\winvb}{{w_1^{-1}(b)}}
\renewcommand{\a}{\alpha}
\renewcommand{\b}{\beta}
\newcommand{\m}{\mu}

@@

We consider the following integro-difference equation
\begin{align}\label{q}
u_{n+1}(x)\;=\;Q[u_n](x)\;:=(k*(g\circ u_n))(x)\;=\,\int^{\infty}_{-\infty}k(x-y)\,g\big(u_n(y)\big)\,\mathrm{d}y,
\end{align}
where 
\begin{equation} \label{g}
g(u) = \begin{cases}
0, & \text{if } u < \a, \\
1, & \text{if } \a \leq u \leq \b, \\
\m, & \text{if } u > \b,
\end{cases}
\end{equation}
with $0<\a<\m<\b<1$. $g(u)$ is a piecewise constant nonmonotone growth function exhibiting a strong Allee effect~\cite{all}. Specifically, it has a stable fixed point at zero and a stable period two cycle $(1,\m)$ with $\a$ the Allee threshold value.

\begin{figure}[h!]
\centering
  \caption{Plot of the growth function $g(u)$ compared to the identity function with growth parameters $\alpha=0.33$, $\beta=0.66$, and $\mu=0.5$.}
  \includegraphics[width=.8\linewidth]{figures/fig1.png}
\end{figure}

@@

Hypothesis (H1) indicates that the dispersal kernel accounts for all individuals, while hypothesis (H2) guarantees the disperal process is symmetric.

@@

 Let $w_1$ and $w_2$ be two functions defined by
\begin{equation} \label{w1}
w_1(x) := \int_x^\infty k(y) \, dy
\end{equation}
and
\begin{equation} \label{w2}
w_2(x) = \int_x^\infty \left( k(y-x_\a) - (1-\mu)k(y-x_\b)\right) \, dy 
\end{equation} 
where $x_\a,x_\b$ and $c^* \in \mathbb R$ are constants given by
\begin{equation}
x_\a =\sup\{x\in\mathbb R\mid w_1(x)\geq\a\}, \quad
x_\b =\sup\{x\in\mathbb R\mid w_1(x)\geq\b\}
\end{equation}
and
\begin{equation}
c^*=\frac{1}{2}\sup\{x\in\mathbb R\mid Q[w_1](x)\geq\a\}
\end{equation}

Note that $c^*$ is finite by the intermediate value theorem since $Q[w_1](\infty)=0$ and $Q[w_1](-\infty)=\m$ with $0<\a<\m$.

\begin{lem} \label{lemma0.5}
$Q[w_1](x) = w_2(x)$ for all $x\in\mathbb R$.
\end{lem}

\begin{proof}
$w_1$ is monotonically decreasing with $w_1(-\infty)=1$ and $w_1(\infty)=0$. It follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$. Applying the integro-difference operator yields
\begin{equation} \label{qw1calculation}
\begin{aligned}
Q[w_1](x) %&= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
&= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \int_{x_\b}^{x_\a} k(x-y) \, dy \\
%&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
&= \int_{x-x_\a}^{\infty} k(y) \, dy - (1-\m) \int_{x-x_\b}^{\infty} k(y) \, dy \\
&= \int_{x}^{\infty} \left(k(y-x_\a)  - (1-\m)k(y-x_\b)\right) \, dy
\end{aligned} \end{equation}
%It can now be seen that replacing $x$ with $x-c^*$ in equation \eqref{w2} produces \eqref{qw1calculation}.
\end{proof}

@@

\begin{lem} \label{lemma1}
If $ ||w_2||_\infty \leq \b$, then $Q[w_2](x)=w_1(x-c^*)$ for all $x\in\mathbb R$.
\end{lem}

\begin{proof}
By Lemma \ref{lemma0}, $w_2(x)$ has either zero or one turning point(s). In the first case, $w_2(x)$ is monotonically decreasing and satisfies $w_2(x) \geq \a$ for $x \leq c^*$ and $w_2(x) < \a$ for $x > c^*$. In the second case, $w_2(x)$ has a unique turning point $x_0 \in \mathbb R$; it follows that $w_2(x)$ is monotonically increasing on $(-\infty,x_0)$ and monotonically decreasing on $(x_0,\infty)$, and $x_0$ is a global maximum. By the assumption $w_2(x)\leq\beta$ for all $x$, we have $w_2(x_0)\leq\beta$. It follows that $c^* \in (x_0,\infty)$, and $w_2(x)$ satisfies $g(w_2(x))=1$ for $x<c^*$ and $g(w_2(x)) = 0$ for $x>c^*$. In both cases, we have

@@

%It follows that $w_2(x)\geq\a$ for $x\leq 2c^*$ and $w_2(x)<\alpha$ for $x>2c^*$. Along with the assumption that $\sup_{x\in\mathbb R}w_2(x)\leq\b$, we can apply the integro-difference operator once more:
\begin{equation} \begin{aligned}
Q[w_2](x) %&= \int_{-\infty}^{\infty} k(x-y) g(w_2(y)) \, dy \\
&= \int_{-\infty}^{c^*} k(x-y) \, dy \\
&= \int_{x-c^*}^{\infty} k(y) \, dy \\
&= w_1(x-c^*).
\end{aligned} \end{equation}
%By defining $c^* = \frac{1}{2}x_0$, and applying the integro-difference operator, we can see that $w_1$ and $w_2$ are both solutions to the periodic traveling wave equation with mean speed $c^*$:
%\begin{equation}
%Q^2[w_1](x) = w_1(x-2c^*); \quad Q^2[w_2](x) = w_2(x-2c^*)
%\end{equation}
\end{proof}

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{figures/fig2A.png}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{figures/fig2B.png}
  \label{fig:sub2}
\end{subfigure}
\caption{The shape of the two periodic traveling wave profiles with Laplace dispersal kernel and growth parameters $\alpha=0.3$, $\mu=0.5$, and $\beta=0.8$.}
\label{fig:test}
\end{figure}

By Lemma \ref{lemma1}, the wave functions $w_1(x)$ and $w_2(x)$ satisfy $Q^2[w_1](x)=w_1(x-2c^*)$ and $Q^2[w_2](x)=w_2(x-2c^*)$. As a result, they can be used to construct a solution to the integral recurrence which spreads in space with a mean speed of $c^*$ and alternates in shape every two time steps. This is formalized in the following theorem:

@@

\begin{equation} \label{ptw}
u_n(x) = \begin{cases}
w_1(x-nc^*) & n \text{ even} \\
w_2(x-nc^*) & n \text{ odd}
\end{cases}
\end{equation}
for all $n \geq 0$.
\end{thm}

\begin{proof}
It suffices to show that equation \eqref{ptw} satisfies $u_{n+1}=Q[u_n]$ for all $n \geq 0$. If $n$ is even, then $n+1$ is odd, so $u_n(x)=w_1(x-nc^*)$ and $u_{n+1}(x)=w_2(x-nc^*-c^*)$. Applying the integro-difference operator, we obtain
\begin{equation} \begin{aligned}
Q[u_n](x) &= Q[w_1](x-nc^*) \\
&= w_2(x-nc^*-c^*) \\
&= u_{n+1}(x)
\end{aligned} \end{equation}
by \eqref{w2}. On the other hand, if $n$ is odd, then $n+1$ is even, so $u_n(x)=w_2(x-nc^*)$ and $u_{n+1}(x)=w_1(x-nc^*-c^*)$. Applying the operator, we get
\begin{equation} \begin{aligned}
Q[u_n](x) &= Q[w_2](x-nc^*) \\
&= Q^2[w_1](x-nc^*+c^*) \\
&= w_1(x-nc^*-c^*) \\
&= u_{n+1}(x)
\end{aligned} \end{equation}
by Lemma \ref{lemma1}.
\end{proof}

@@

\begin{figure}[h!] 
\centering
  \caption{Numerical simulation of the integro-difference equation with Laplace dispersal kernel, $\alpha=0.2$, $\mu=0.3$, and $\beta=0.8$. Later timepoints are colored in red, with earlier timepoints colored in green.}
\label{fig3}
  \includegraphics[width=.8\linewidth]{figures/fig3.png}
\end{figure}

Figure \ref{fig3} shows the propagation of the periodic traveling wave solution for a particular choice of dispersal kernel and growth parameters.

>>>>

\newcommand{\winva}{{w_1^{-1}(a)}}
\newcommand{\winvb}{{w_1^{-1}(b)}}
\renewcommand{\a}{a}
\renewcommand{\b}{b}
\newcommand{\m}{n_1}
\newcommand{\mtwo}{n_2}

@@

We consider the following integro-difference equation
\begin{align}\label{q}
u_{n+1}(x)\;=\;Q[u_n](x)\;:=(k*(g\circ u_n))(x)\;=\,\int^{\infty}_{-\infty}k(x-y)\,g\big(u_n(y)\big)\,\mathrm{d}y,
\end{align}
where 
\begin{equation} \label{g}
g(u) = \begin{cases}
0, & \text{if } u < \a, \\
\mtwo, & \text{if } \a \leq u \leq \b, \\
\m, & \text{if } u > \b,
\end{cases}
\end{equation}
with $0<\a<\m<\b<1$. $g(u)$ is a piecewise constant nonmonotone growth function exhibiting a strong Allee effect~\cite{all}. Specifically, it has a stable fixed point at zero and a stable period two cycle $(1,\m)$ with $\a$ the Allee threshold value.

\begin{figure}[h!]
\centering
  \caption{Plot of the growth function $g(u)$ compared to the identity function with growth parameters $\a=0.33$, $\b=0.66$, and $\m=0.5$, and $\mtwo=1.0$.}
  \includegraphics[width=.8\linewidth]{figures/fig1.png}
\end{figure}

@@

@@

 Let $w_1$ and $w_2$ be two functions defined by
\begin{equation} \label{w1}
w_1(x) := \int_x^\infty \mtwo k(y) \, dy
\end{equation}
and
\begin{equation} \label{w2}
w_2(x) = \int_x^\infty \left( \mtwo k(y-x_\a) - (\mtwo-\m)k(y-x_\b)\right) \, dy 
\end{equation} 
where $x_\a$ and $x_\b$ constants constants given by
\begin{equation}
x_\a =\sup\left\{x\in\mathbb R\mid \int_{-\infty}^{x} k(y) \, dy \leq \frac{\a}{\mtwo} \right\}, \quad
x_\b =\sup\left\{x\in\mathbb R\mid \int_{-\infty}^{x} k(y) \, dy \leq \frac{\b}{\mtwo} \right\}
\end{equation}

\begin{lem} \label{lemmamain}
If $ || w_2 ||_\infty \leq \b $, then $w_1$ and $w_2$ satisfy
\begin{equation}
Q[w_1](x) = w_2(x)
\end{equation}
and
\begin{equation}
Q[w_2](x) = w_1(x-2c^*)
\end{equation}
for all $x\in\mathbb R$, where $c^*$ is a constant given by
\begin{equation}
c^* = \frac{1}{2} \sup\{x\in\mathbb R\mid w_2(x)\geq \a\}
\end{equation}
\end{lem}

%
%
%\begin{lem} \label{lemma0.5}
%$Q[w_1](x) = w_2(x)$ for all $x\in\mathbb R$.
%\end{lem}

\begin{proof}
$w_1$ is monotonically decreasing with $w_1(-\infty)=\mtwo$ and $w_1(\infty)=0$. It follows that $w_1(x)>\b$ for $x<x_\b$, $\a\leq w_1(x)\leq\b$ for $x_\b\leq x\leq x_\a$, and $w_1(x)<\a$ for $x>x_\a$. This yields
\begin{equation}
g(w_1(x)) = \begin{cases}
\m & x < x_\b \\
\mtwo & x_\b \leq x \leq x_\a \\
0 & x > x_\a
\end{cases}
\end{equation}
Applying the integro-difference operator yields
\begin{equation} \label{qw1calculation}
\begin{aligned}
Q[w_1](x) &= \int_{-\infty}^{\infty} k(x-y) g(w_1(y)) \, dy \\
&= \m \int_{-\infty}^{x_\b} k(x-y) \, dy + \mtwo \int_{x_\b}^{x_\a} k(x-y) \, dy \\
%&= \m \int_{x-x_\b}^{\infty} k(y) \, dy + \int_{x-x_\a}^{x-x_\b} k(y) \, dy \\
&= \mtwo \int_{x-x_\a}^{\infty} k(y) \, dy - (\mtwo-\m) \int_{x-x_\b}^{\infty} k(y) \, dy \\
&= \int_{x}^{\infty} \left( \mtwo k(y-x_\a)  - (\mtwo-\m)k(y-x_\b)\right) \, dy
\end{aligned} \end{equation}
%It can now be seen that replacing $x$ with $x-c^*$ in equation \eqref{w2} produces \eqref{qw1calculation}.
%\end{proof}

@@

%\begin{lem} \label{lemma1}
%If $ ||w_2||_\infty \leq \b$, then $Q[w_2](x)=w_1(x-c^*)$ for all $x\in\mathbb R$.
%\end{lem}

%'\begin{proof}
By Hypothesis (H4), we have assumed that the integrand on the right hand side has at most one zero. We can now proceed in cases. $w_2(x)$ has either zero or one turning point(s). In the first case, $w_2(x)$ is monotonically decreasing and satisfies $w_2(x) \geq \a$ for $x \leq 2c^*$ and $w_2(x) < \a$ for $x > 2c^*$. In the second case, $w_2(x)$ has a unique turning point $x_0 \in \mathbb R$; it follows that $w_2(x)$ is monotonically increasing on $(-\infty,x_0)$ and monotonically decreasing on $(x_0,\infty)$, and $x_0$ is a global maximum. By the assumption $w_2(x)\leq\beta$ for all $x$, we have $w_2(x_0)\leq\beta$. It follows that $c^* \in (\frac{x_0}{2},\infty)$, and $w_2(x)$ satisfies $g(w_2(x))=1$ for $x<2c^*$ and $g(w_2(x)) = 0$ for $x>2c^*$. In both cases, we have

\begin{equation}
g(w_2(x)) = \begin{cases}
1 & x \leq 2c^* \\
0 & x > 2c^*
\end{cases}
\end{equation}

@@

%It follows that $w_2(x)\geq\a$ for $x\leq 2c^*$ and $w_2(x)<\alpha$ for $x>2c^*$. Along with the assumption that $\sup_{x\in\mathbb R}w_2(x)\leq\b$, we can apply the integro-difference operator once more:
Thus,
\begin{equation} \begin{aligned}
Q[w_2](x) &= \int_{-\infty}^{\infty} k(x-y) g(w_2(y)) \, dy \\
&= \int_{-\infty}^{2c^*} k(x-y) \, dy \\
&= \int_{x-2c^*}^{\infty} k(y) \, dy \\
&= w_1(x-2c^*).
\end{aligned} \end{equation}
%By defining $c^* = \frac{1}{2}x_0$, and applying the integro-difference operator, we can see that $w_1$ and $w_2$ are both solutions to the periodic traveling wave equation with mean speed $c^*$:
%\begin{equation}
%Q^2[w_1](x) = w_1(x-2c^*); \quad Q^2[w_2](x) = w_2(x-2c^*)
%\end{equation}
\end{proof}

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{figures/fig2A.png}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{figures/fig2B.png}
  \label{fig:sub2}
\end{subfigure}
\caption{The shape of the two periodic traveling wave profiles with Laplace dispersal kernel and growth parameters $\a=0.3$, $\m=0.5$, and $\b=0.8$.}
\label{fig:test}
\end{figure}

By Lemma \ref{lemmamain}, the wave functions $w_1(x)$ and $w_2(x)$ satisfy $Q^2[w_1](x)=w_1(x-2c^*)$ and $Q^2[w_2](x)=w_2(x-2c^*)$. As a result, they can be used to construct a solution to the integral recurrence which spreads in space with a mean speed of $c^*$ and alternates in shape every two time steps. This is formalized in the following theorem:

@@

\begin{equation} \label{ptw}
u_n(x) = \begin{cases}
w_1(x-nc^*) & n \text{ even} \\
w_2(x-nc^*+c^*) & n \text{ odd}
\end{cases}
\end{equation}
for all $n \geq 0$.
\end{thm}

\begin{proof}
It suffices to show that equation \eqref{ptw} satisfies $u_{n+1}=Q[u_n]$ for all $n \geq 0$. If $n$ is even, then $n+1$ is odd, so $u_n(x)=w_1(x-nc^*)$ and $u_{n+1}(x)=w_2(x-nc^*)$. Applying the integro-difference operator, we obtain
\begin{equation} \begin{aligned}
Q[u_n](x) &= Q[w_1](x-nc^*) \\
&= w_2(x-nc^*) \\
&= u_{n+1}(x)
\end{aligned} \end{equation}
by \eqref{w2}. On the other hand, if $n$ is odd, then $n+1$ is even, so $u_n(x)=w_2(x-nc^*+c^*)$ and $u_{n+1}(x)=w_1(x-nc^*-c^*)$. Applying the operator, we get
\begin{equation} \begin{aligned}
Q[u_n](x) &= Q[w_2](x-nc^*+c^*) \\
&= w_1(x-nc^*-c^*) \\
&= u_{n+1}(x)
\end{aligned} \end{equation}
by Lemma \ref{lemmamain}.
\end{proof}

@@

\begin{figure}[h!] 
\centering
  \caption{Numerical simulation of our model using the Laplace dispersal kernel. The parameters chosen for this simulation were $\a=0.2$, $\m=0.3$, and $\b=0.8$, and $\mtwo=1.0$. Later timepoints are colored in red, with earlier timepoints colored in green.}
\label{fig3}
  \includegraphics[width=.8\linewidth]{figures/fig3.png}
\end{figure}

The previous theorem shows that our model can exhibit a periodic traveling wave solution with alternating wave profiles. Furthermore, we derived a constant wave speed at which the oscillating pair of waves travels. We now turn our attention to the magnitude of the oscillation in the wave speed. For a sufficiently small $\ell > 0$, we may label the point of intersection of the curve $u=u_n(x)$ with the horizontal line $u=\ell$ by $\xi_{n,\ell}$, or simply $\xi_n$. It follows that $\xi_1,\xi_2,\xi_3,\dots\to\infty$ as $n\to\infty$; furthermore, the previous theorem implies that for any $\ell$, we have $\xi_{n+2}-\xi_n=2c^*$ for every $n\geq 1$.

For every $n\geq 1$, let $c_n = \xi_n - \xi_{n-1}$.
